Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-04 nlpcc/paper.tex
自己改了一半

Cross-lingual Knowledge Bases are important for global knowledge sharing. However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy. In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems. The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike. An extension method is used to increase language links while a pruning approach is used to refine taxonomy. Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB. Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.

@@

\section{Introduction}
With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing. Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge} and many other applications. These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.

@@

A cross-lingual knowledge base can effectively promote global knowledge sharing, understanding and expanding. However, to build an practical knowledge base, some problems must be addressed: (1) The imbalance of different language source size leads to less entities. Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging. (2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base. Statistically, only XX\% articles have cross-lingual links between English and Chinese in all articles of the two languages. Especially scarce evident links for infobox attribute. (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example,\textcolor{red}{example}

@@

Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike. To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information. In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX classes, XXX instances and XXX properties. During the whole procedure, we also expand language links and make judgement on the semantic relations. Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our knowledge base. Specifically, our work makes the following contributions:
\begin{itemize}
  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedia. Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
  \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{itemize}

The rest of the paper is organized as follows. Section \ref{sec:pd} introduces the related classes and defines the problem of building a cross-lingual knowledge base. Section \ref{sec:dp} presents the extraction approaches in class, instance and property level. Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result. Section \ref{sec:result} demonstrates the data situation of established knowledge base. Section \ref{sec:work} reviews the related literatures. Section \ref{sec:con} concludes this paper and points out some future directions of this work.

@@

\subsection{Wiki Pages}
Articles from the four sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy. An article describes an entity with rich information created and modified by several verified editors. Besides, each article is linked to one or more categories by \textit{articleOf} relation. In general, there are five elements can be exploited in each article page:
\begin{figure}
    \centering
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
        \caption{Taxonomy in Hudong}
        \label{fig:hudong-taxonomy}
    \end{minipage}%
\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are subject-attribute-value triples formalized as a table. Information in this table includes important properties of an entity.
  \item Links: Links are entries to other articles within the encyclopedia. They lead readers to reference articles. Actually, they represent the relations between the current article and other articles.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

@@

Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited. A template defines items that a group of article should fill. Besides, infoboxes are also generated based on certain templates recommended by Wikipedia. For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films. An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}. We denote infobox template as $T(a)$. Templates specify certain attributes, which are usually different from those displayed on the webpage. Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value. The value maybe a text or a reference to another entity.

Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article. Fig. \ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page. As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately. Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.

@@

A cross-lingual knowledge base is a database conform to a cross-lingual ontology. Taking advantage of language links in $CL$, several monolingual-ontologies generated from various sources can be merge into one cross-lingual ontology.  Thus a knowledge base can be defined as:
\begin{equation}
    KB = <O_{i}, CL>
\end{equation}
where $O_{i}$ denotes the ith monolingual-ontology, $CL$ represents the cross-lingual link set.

@@

In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources. Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting. We then enrich the extracted language-link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.

The whole building procedure is shown in Fig. \ref{fig:procedure}
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
    \caption{Procedure of building our cross-lingual knowledge base}
    \label{fig:procedure}
\end{figure}%
We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed. After data parsing, we get four ontologies each source. Going through the process of taxonomy pruning, we delete some incorrect relations. At last Using the extended language links, we combine the four ontologies into a cross-lingual knowledge base.

\section{Semantic Data Extraction}
\label{sec:dp}
Semantic data extraction aims to achieve a structured dataset from the input encyclopedias, preparing for the knowledge base construction. Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.

@@

\subsubsection{General-properties}
Characteristics of an entity are regarded as general-properties, including label, abstract, and url. General-properties describe general information of an entity. We define three datatype properties as general-properties for a given article $a$: (1) label property; (2) abstract property; (3) URL property.

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file. Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Interstellar}' infobox. The left is infobox, the middle is a snap from dump file in Wikipedia. As we've seen, attribute label in infobox is different from it in dump file. We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
        \label{fig:infobox-template}
    \end{figure}%
\item There are special characters in labels. Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels. For example, \emph{population} property has sub-properties "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

@@

We harvest four types of information during this stage. (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value. (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page. For example, 美国科幻片(American science fiction films) is a category of Interstellar; (4) Reference relation with other instances according to links in the content. We gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).

@@

To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate. At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.

\subsection{Cross-lingual Linking}
There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label. That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.

>>>>

Cross-lingual Knowledge Bases are important for global knowledge sharing. However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy. In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems. The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike. An extension method is used to increase language links while a pruning approach is used to refine taxonomy. Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB. Moreover, the paper provides webpages for knowledge visualization and a SPARQL endpoint accessing to the established CLKB.

@@

\section{Introduction}
With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing. Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{fernandez2011generic,kaminskas2012knowledge} and many other applications. These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.

@@

A cross-lingual knowledge base can effectively promote global knowledge sharing, understanding and expanding. However, to build an practical knowledge base, some problems must be addressed: (1) The imbalance of different language source size leads to less entities. Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand respectively, it's obvious that structuring a Chinese knowledge base based on Wikipedia-only is difficult. (2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base. Statistically, only XX\% articles have Chinese-English links among all articles in the two languages. (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example,\textcolor{red}{example}

@@

Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike. To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information. In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base(CLKB), which contains XXX classes, XXX instances and XXX properties. During the whole procedure, we also expand language links and make judgement on the semantic relations. Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our CLKB. Specifically, our work makes the following contributions:
\begin{itemize}
  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedia. Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
  \item We extend the language link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to obtain more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
  \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{itemize}

The rest of the paper is organized as follows. Section \ref{sec:pd} introduces the related concepts and defines the problem of building a CLKB. Section \ref{sec:dp} presents the extraction approaches in class, instance and property level. Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result. Section \ref{sec:result} demonstrates the data situation of established knowledge base. Section \ref{sec:work} reviews the related literatures. Section \ref{sec:con} concludes this paper and points out some future directions of this work.

@@

\subsection{Wiki Pages}
Articles from wiki sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy. An article describes an entity with rich information created and modified by several verified editors. Besides, each article is linked to one or more categories by \textit{articleOf} relation. In general, there are six elements can be exploited in each article page:
\begin{figure}
    \centering
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
        \caption{Taxonomy in Hudong}
        \label{fig:hudong-taxonomy}
    \end{minipage}%
\end{figure}
\begin{itemize}
  \item Title: A title is the label of an entity, which is unique so that it can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are subject-attribute-value triples formalized as a table. Information in this table includes important properties of an entity.
  \item Links: Links are entries to other articles within the encyclopedia. They represent the relations between the current article and others.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

@@

Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited. A template defines items that a group of article should fill. Besides, infoboxes are also generated based on certain templates recommended by Wikipedia. For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films. An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}. We denote infobox template used in article $a$ as $T(a)$. Templates specify certain attributes, which are usually different from those displayed on the webpage. Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value. The value maybe a text or a reference to another entity.

Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article. Fig. \ref{fig:interstellar}shows language links of \emph{Interstellar} on the left column of the Wikipedia page. As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese respectively. Thus, to a $cl \in CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.

@@

A Cross-lingual Knowledge Base(CLKB) is a database conform to a cross-lingual ontology. Taking advantage of language links in $CL$, several monolingual-ontologies generated from various sources can be merge into one cross-lingual ontology.  Thus a knowledge base can be defined as:
\begin{equation}
    KB = <O_{i}, CL>
\end{equation}
where $O_{i}$ denotes the ith monolingual-ontology, $CL$ represents the cross-lingual link set.

@@

In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese encyclopedia sources. Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting. We then enrich the extracted language-link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an Chinese-English ontology with SPARQL endpoint through process of combining $O_{i}$ by utilizing language links in $CL$.

The whole building procedure is shown in Fig. \ref{fig:procedure}
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
    \caption{Procedure of building our cross-lingual knowledge base}
    \label{fig:procedure}
\end{figure}%
We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed. After data parsing, we get four ontologies each source. Going through the process of taxonomy pruning, we delete some incorrect relations. At last using the extended language links, we combine the four ontologies into our .

\section{Semantic Data Extraction}
\label{sec:dp}
Semantic data extraction aims to achieve a structured dataset from the input encyclopedias. Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and their templates.

@@

\subsubsection{General-properties}
Characteristics of an entity are regarded as general-properties, including label, abstract, and url. General-properties describe general information of an entity. We define three datatype properties as general-properties for a given article: (1) label property; (2) abstract property; (3) URL property.

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) is an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file. Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Interstellar}' infobox. The left is infobox, the middle is a snap from dump file in Wikipedia. We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
        \label{fig:infobox-template}
    \end{figure}%
\item There are special characters in labels. Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels. For example, attribute \emph{population} has sub-attribute "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong attribute labels by mistake.
\end{itemize}

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. Rright of Fig.\ref{fig:infobox-template} shows an example of template \emph{Infobox film}, where corresponding relations of display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

@@

We harvest four types of information during this stage: (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value. (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page. For example, \textit{美国科幻片(American science fiction films)} is a category of \textit{Interstellar}; (4) Reference relation $Li(a)$ with other instances according to links in the content, such as \textit{华纳兄弟(Warner Bros.)} of \textit{Interstellar}.

@@

To construct a CLKB with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from classes relationships to make it more accurate.

\subsection{Cross-lingual Linking}
There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus we take the following steps to solve the problem: (1) Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label. That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
